\sloppy 
\chapter{Bibliography}

\referencewebsite{1}{WHO}{Falls}{World Health Organization}{2018}{\href{https://www.who.int/news-roo#m/fact-sheets/detail/falls}{https://www.who.int/news-roo#m/fact-sheets/detail/falls}}

\referenceArticle{2}{R. Luque, E. Casilari, M.-J. Mor´on, G. Redondo}{Comparison and Characterisation of Android-Based Fall Systems, Sensors 14}{IEEE}{2014}{18543-18574}

\referenceArticle{3}{S. S. Khan, J. Hoey}{Review of Fall Detection Techniques: a Data Availability Perspective}{University of Waterloo}{2016}{pp.6, 8-9, 12, 19}

\referenceArticle{4}{L. Schwickert, C. Becker, U. Lindemann, C. Mar´echal, A. Bourke, L. Chiari, J. Helbostad, W. Zijlstra, K. Aminian, C. Todd, S. Bandinelli, J. Klenk}{Fall detection with body-worn sensors: a systematic review, Zeitschrift f¨ur Gerontologie und Geriatrie}{IEEE}{2013}{706–719}

\referencewebsite{5}{B. Marr}{Facial Recognition Technology: Here Are The Important Pros and Cons}{Forbes}{2019}{\href{https://www.forbes.com/sites/bernardmarr/2019/08/19/facial-recognition-technology-here-are-the-important-pros-and-cons}{https://www.forbes.com/sites/bernardmarr/2019/08/19/facial-recognition-technology-here-are-the-important-pros-and-cons}}

\referencewebsite{6}{healthdirect}{Falls and The Elderly}{healthdirect}{2020}{\href{https://www.healthdirect.gov.au/falls}{https://www.healthdirect.gov.au/falls}}

\referencewebsite{7}{Stay On Your Feet}{Falls facts
}{Stay On Your Feet}{2021}{\href{https://www.stayonyourfeet.com.au/over60/what-can-cause-a-fall/falls-facts/}{https://www.stayonyourfeet.com.au/over60/what-can-cause-a-fall/falls-facts/}}

\referenceArticle{8}{R. W. Broadley, J. Klenk, S. B. Thies, L. P.J. Kenney, M. H. Granat}{Methods For The Real-World Evaluation of Fall Detection Technology: a Scoping Review}{MDPI}{2018}{pp. 1-3}

\referencewebsite{9}{CDC}{Cost of Older Adult Falls}{Centers for Disease Control}{2020}{https://www.cdc.gov/homeandrecreationalsafety/falls/data/fallcost.html}

\referencewebsite{10}{J. Fleming, C. Brayne}{Inability To Get Up After Falling, Subsequent Time On Floor, and Summoning Help: Prospective Cohort Study in People Over 90}{BMJ}{2008}{pp. 1, 3-4}

\referencewebsite{11}{Medical Alert Advice}{Is The Apple Watch Series 4, 5 or 6 With Fall Detection Right For You?}{Medical Alert Advice}{2021}{\href{https://www.medicalalertadvice.com/articles/apple-watch-fall-detection/}{https://www.medicalalertadvice.com/articles/apple-watch-fall-detection/}}

\referenceArticle{12}{A. Shahzad, K. Kim}{FallDroid: an Automated Smart Phone Based Fall Detection System Using Multiple Kernel Learning}{IEEE}{2018}{pp. 1-2, 9}

\referenceArticle{13}{G. W. Lindsay}{Convolutional Neural Networks as a Model of The Visual System: Past, Present, and Future}{J Cogn Neurosci}{2020}{pp. 3-5}

\referenceArticle{14}{S. Ji, M. Yang, K. Yu}{3D Convolutional Neural Networks
For Human Action Recognition}{IEEE}{2013}{pp. 221-230}

\referenceArticle{15}{A. Núñez-Marcos, G. Azkune, I. Ignacio Arganda-Carreras}{Vision-Based Fall Detection With Convolutional Neural Networks}{Hindawi}{2017}{pp. 221-230}

\referenceArticle{16}{J. Arunnehru, G. Chamundeeswari, S. P. Bharathi}{Human Action Recognition Using 3D Convolutional Neural Networks With 3D Motion Cuboids in Surveillance Videos}{ScienceDirect}{2018}{pp. 472-477}

\referenceArticle{17}{F. Jin, R. Zhang, A. Sengupta, S. Cao, S. Hariri, N. K. Agarwal, S. K. Agarwal}{Multiple Patients Behavior Detection in Real-time Using mmWave Radar and Deep CNNs}{IEEE}{2019}{pp. 1-5}

\referenceArticle{18}{L. Palmerini, J. Klenk, C. Becker, L. Chiari}{Accelerometer-Based Fall Detection Using Machine Learning: Training and Testing on Real-World Falls}{MDPI}{2020}{pp. 2-15}

\referenceArticle{19}{I. J. Goodfellow, J. Shlens & C. Szegedy}{Explaining and Harnessing Adversarial Examples}{ICLR}{2015}{pp. 1-6}

\referencewebsite{20}{Abacus.AI}{The Intuition Behind Variational Autoencoders}{Abacus.AI}{2020}{\href{https://medium.com/@realityenginesai/understanding-variational-autoencoders-and-their-applications-81a4f99efc0d}{https://medium.com/@realityenginesai/understanding-variational-autoencoders-and-their-applications-81a4f99efc0d}}

\referenceArticle{21}{F. Jin, A. Sengupta, S. Cao}{mmFall: Fall Detection Using 4D MmWave Radar and a Hybrid Variational RNN AutoEncoder}{IEEE}{2020}{pp. 1-10}

\referenceArticle{22}{C. Medrano, R. Igual, I. Plaza, M. Castro}{Detecting Falls as Novelties in Acceleration Patterns Acquired With Smartphones}{PloS one}{2012}{pp. 1-9}

\referenceArticle{23}{M. Yu, Y. Yu, A. Rhuma, S. M. R. Naqvi, L. Wang, J. A. Chambers}{An Online One Class Support Vector Machine-Based Person-Specific Fall Detection System For Monitoring an Elderly Individual in a Room Environment}{IEEE}{2013}{pp. 1002–1014}

\referenceArticle{24}{J. Nogas, S. S. Khan, A. Mihailidis}{DeepFall – Non-invasive Fall Detection With Deep Spatio-Temporal Convolutional Autoencoders}{arXiv}{2020}{pp. 1–18}

\referencewebsite{25}{C. Lovescu, S. Rao}{mmWave Radar Sensors - What Is mmWave}{Texas Instruments}{2020}{\href{https://www.ti.com/sensors/mmwave-radar/what-is-mmwave.html}{https://www.ti.com/sensors/mmwave-radar/what-is-mmwave.html}}

\referenceArticle{26}{C. Lovescu, S. Rao}{The Fundamentals of Millimeter Wave Sensors}{Texas Instruments}{2020}{pp. 1-9}

\referenceArticle{27}{G. Koshmak, M. Lindén, A. Loutfi}{Challanges and Issues in Multisensor Fusion Approach For Fall Detection: Review Paper}{Hindawi}{2015}{pp. 1-12}

\referenceArticle{28}{G. Pang, C. Shen, L. Cao, A. V. D. Hengel}{Deep Learning for Anomaly Detection: a Review}{arXiv}{2020}{pp. 1-36}

\referenceArticle{29}{B. R. Kiran, D. M. Thomas, R. Parakkal}{An Overview of Deep Learning Based Methods For Unsupervised and Semi-Supervised Anomaly Detection in Videos}{MDPI}{2018}{pp. 1-25}

\referenceArticle{30}{Y. Karadayi, M. N. Aydin, A. S. Ö˘grenci}{A Hybrid Deep Learning Framework for Unsupervised Anomaly Detection in Multivariate Spatio-Temporal Data}{MDPI}{2020}{pp. 1-25}

\referencewebsite{31}{Rocca J.}{Understanding Variational Autoencoders (VAEs).}{towards data science}{2020}{\href{https://towardsdatascience.com/understanding-variational-autoencoders-vaes-f70510919f73}{https://towardsdatascience.com/understanding-variational-autoencoders-vaes-f70510919f73}}
https://towardsdatascience.com/understanding-variational-autoencoders-vaes-f70510919f73

\referencewebsite{32}{Google}{Classification: Precision and Recall}{Google}{2020}{\href{https://developers.google.com/machine-learning/crash-course/classification/precision-and-recall}{https://developers.google.com/machine-learning/crash-course/classification/precision-and-recall}}

\referencewebsite{33}{Dembla G.}{Intuition behind Log-loss score}{Towards Data Science}{2020}{\href{https://towardsdatascience.com/intuition-behind-log-loss-score-4e0c9979680a}{https://towardsdatascience.com/intuition-behind-log-loss-score-4e0c9979680a}}